Weighted Model Counting/Integration from the Perspective of Boolean Algebras

### 2020-03-24 paper.tex
Proof of the lemma

\begin{definition}[\cite{DBLP:books/daglib/0090259,levasseur2012applied}]
  An element $a \ne 0$ of $\mathbf{B}$ is an \emph{atom} if, for all $x \in
  \mathbf{B}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne
  0$ is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$. A BA
  $\mathbf{B}$ is \emph{atomic} if for every $a \in \mathbf{B} \setminus \{0
  \}$, there is an atom $x$ such that $x \le a$.
\end{definition}

@@

% TODO: Start here. Define filters (ref the undergraduate book), filter
% generation (same ref, but read it first), and quotients.
\begin{definition}
\end{definition}

@@

\begin{lemma}
  Let $\mathbf{B}$ be a BA, and let $F$ be a filter in $\mathbf{B}$ generated by
  $p \in \mathbf{B}$. Then, for any $a, b \in \mathbf{B}$, if $a/F = b/F$, then
  $a \land p = b \land p$.
\end{lemma}
\begin{proof}
  % TODO: reference for a/F = b/F iff a <-> b \in F
  % TODO: reference for the definition of a filter
\end{proof}

\begin{definition}[Measures on quotients] \label{def:measures_on_quotients}
  Let $\mathbf{B}$ be a BA with a measure $m : \mathbf{B} \to \mathbb{R}_{\ge
    0}$, and let $F$ be a filter in $\mathbf{B}$ generated by some $p \in
  \mathbf{B}$. We can define a measure $m^*$ on $\mathbf{B}/F$ as
  \[
    m^*([a]) = m(a \land p).
  \]
\end{definition}

\begin{proposition}
  The function $m^*$ in \cref{def:measures_on_quotients} is well-defined.
  Furthermore, if $m$ is a WMC measure, then so is $m^*$.
\end{proposition}
\begin{proof}
\end{proof}
% TODO: prove that the two ways to compute the probability give the same answer.

% Feedback: Clarify the relationship between $\nWMC$ and the probability induced
% by a WMC formulation.

>>>>

\begin{definition}[\cite{DBLP:books/daglib/0090259,levasseur2012applied}]
  An element $a \ne 0$ of $\mathbf{B}$ is an \emph{atom} if, for all $x \in
  \mathbf{B}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne
  0$ is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$. The BA
  $\mathbf{B}$ is \emph{atomic} if for every $a \in \mathbf{B} \setminus \{0
  \}$, there is an atom $x$ such that $x \le a$.
\end{definition}

@@

\begin{definition}[\cite{givant2008introduction}] \label{def:filter}
  A \emph{(Boolean) filter} is a non-empty subset $F \subseteq \mathbf{B}$ such
  that
  \begin{itemize}
  \item $f \land g \in F$ for all $f, g \in F$,
  \item $f \lor a \in F$ for all $f \in F$ and $a \in \mathbf{B}$.
  \end{itemize}
  For any $p \in \mathbf{B}$, the \emph{principal filter of $p$} is the
  intersection $I$ of all filters that contain $p$. It also has the property
  that $p \le a$ for all $a \in I$.
\end{definition}

\begin{definition}[\cite{sikorski1969boolean}] \label{def:quotient}
  Let $F \subseteq \mathbf{B}$ be a filter. The \emph{quotient} $\mathbf{B}/F$
  is a BA of equivalence classes of elements of $\mathbf{B}$ with respect to the
  equivalence relation
  \[
    a \sim b \qquad \iff \qquad a \to b \in F \quad \text{and} \quad b \to a \in F
  \]
  for all $a, b \in \mathbf{B}$. Elements of $\mathbf{B}/F$ are usually denoted
  by $a/F$ (for some $a \in \mathbf{B}$) with the understanding that if $b \sim
  a$ (for some $b \in \mathbf{B}$), then $b/F = a/F$.
\end{definition}

@@

\begin{lemma}
  Let $\mathbf{B}$ be a BA, and let $F$ be the principal filter of $p \in
  \mathbf{B}$. Then, for any $a, b \in \mathbf{B}$, if $a/F = b/F$, then $a
  \land p = b \land p$.
\end{lemma}
\begin{proof}
  If $a/F = b/F$, then $a \to b \in F$ by \cref{def:quotient}. Then $p \le a \to
  b$ by \cref{def:filter}, and $(a \to b) \land p = p$ by the definition of
  $\le$. Then
  \[
    1 = p \lor \neg p = ((a \to b) \lor \neg p) \land (p \lor \neg p) = \neg a
    \lor b \lor \neg p = \neg (a \land p) \lor b.
  \]
  So
  \[
    \neg b = (\neg(a \land p) \land \neg b) \lor (b \land \neg b) = \neg((a
    \land p) \lor b),
  \]
  and thus $b = (a \land p) \lor b$, and
  \[
    b \land p = (a \land p) \lor (b \land p) = (a \lor b) \land p.
  \]
  Similarly, $a \land p = (a \lor b) \land p$ which proves that $a \land p = b
  \land p$.
\end{proof}

\begin{proposition}[Measures on quotients] \label{def:measures_on_quotients}
  Let $\mathbf{B}$ be a BA with a measure $m : \mathbf{B} \to \mathbb{R}_{\ge
    0}$, and let $F$ be the principal filter of $p \in \mathbf{B}$. Let us
  define $m^*\colon \mathbf{B}/F \to \mathbb{R}_{\ge 0}$ as
  \[
    m^*(a/F) = m(a \land p)
  \]
  for any $a \in \mathbf{B}$. The function $m^*$ is well-defined. Furthermore,
  if $m$ is a WMC measure, then so is $m^*$.
\end{proposition}

% TODO: prove that the two ways to compute the probability give the same answer.
